Aggressive Scheduling for Numerical Programs

### 2012-05-02 report/draft.tex
added schedule template
wrote up "putting it all together"... less than pleased, need more sleep.

\subsection{Enforcing a Schedule}
\begin{comment}
+(X) How do we enforce a schedule at the C level?
+( ) What does the code look like?
+(X) Would this hack always work? Either way it would be ideal to have a flag
     or pragma to allow the user to choose a schedule.

@@

\subsection{Putting it all Together}
\begin{verbatim}
+( ) Requirements of the code before we can SP (what optimizations should we
  do/evaluate automatically?)

>>>>

\subsection{Enforcing a Schedule}
\begin{comment}
+(X) How do we enforce a schedule at the C level?
+(X) What does the code look like?
+(X) Would this hack always work? Either way it would be ideal to have a flag
     or pragma to allow the user to choose a schedule.

@@

\subsection{Putting it all Together}
\begin{comment}
+( ) Requirements of the code before we can SP (what optimizations should we
  do/evaluate automatically?)
\end{comment}
% NOTE: in the future when we submit this somewhere the following section
% should not be a steaming pile. shame on richard

Through the ability to apply software pipelining on any loop in SPIRAL and a
mechanism to enforce scheduling we can tailor a schedule of any
operation written in ICode to a given system. Currently, our optimizations for
tailoring software pipelining include strip-mining, reordering and unrolling the
outer loops before we perform the actual scheduling. These few optimization
provide a great degree of freedom with respect to tuning an implementation to
a system.

However, our current system is not without limitations. Because we are
attempting to schedule at a high level, our ICode implementation must map to the
underlying Instruction Set Architecture(ISA). Furthermore, our method
restricts the quality of optimizations that the compiler can provide, thus the
ICode must be aggressively optimized. Fortunately, SPIRAL was designed with
the necessary facilities in place for this level of optimization.
